---
title             : "Aggregation Experiment 2 - Summary"
shorttitle        : ""

note              : Created `r format(Sys.time())`

author: 
  - name          : "Shir Dekel"
  
floatsintext      : yes

bibliography      : '`r system.file("refs.bib", package = "shiR")`'
csl               : '`r system.file("apa.csl", package = "shiR")`'
documentclass     : "apa7"
classoption       : "man, donotrepeattitle"
output: 
  papaja::apa6_pdf:
    includes: 
      in_header: "preamble.tex"
---

```{r setup, include = FALSE}
opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
loadd(descriptives)
loadd(analysis_proportion)
loadd(analysis_choice)
```

```{r allocation}
descriptives$allocation %>% 
  apa_table("Group allocation to the between-subject variables of awareness, presentation, and distribution.")
```

# Results

There are two ways that I can see of analysing these data: as binary choice per trial (using logistic regression), or as proportions of choice per participant (using t-test). The logistic regression should theoretically account for more variance than the t-test, but the estimates are less interpretable.

Figures\ \@ref(fig:plot-choice) and\ \@ref(fig:plot-proportion) show the choice and proportion data, respectively. The difference between presentation conditions was not significant, both in the logistic regression `r analysis_choice$presentation$full_result$presentationjoint`, and in the t-test, `r analysis_proportion$presentation`. However, those that that saw a distribution tended to choose to invest significantly more than those that did not see a distribution, seen both in the logistic regression, `r analysis_choice$distribution$full_result$distributionpresent`, and the t-test `r analysis_proportion$distribution`.

```{r plot-choice, fig.cap = "Choice data"}
readd(choice_plot)
```

```{r plot-proportion, fig.cap = "Proportion data"}
readd(proportion_plot)
```

```{r plot-portfolio-number, fig.cap = "Portfolio number data"}
readd(portfolio_number_plot)
```

```{r plot-portfolio-binary, fig.cap = "Portfolio binary data"}
readd(portfolio_binary_plot)
```

\newpage

# References

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
