---
title             : "Aggregation Experiment 2 materials"
shorttitle        : ""

note              : Created `r format(Sys.time())`

author: 
  - name          : "Shir Dekel"
  
floatsintext      : yes

bibliography      : '`r system.file("refs.bib", package = "shiR")`'
csl               : '`r system.file("apa.csl", package = "shiR")`'
documentclass     : "apa7"
classoption       : "man, donotrepeattitle"
output: 
  papaja::apa6_pdf:
    includes: 
      in_header: "preamble.tex"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Demographics

Figure\ \@ref(fig:demographics) shows page 1 of the demographics. Figure\ \@ref(fig:business) shows the business-specific questionnaire that participants see if they select "Yes" to the last question on page 1. Figures\ \@ref(fig:sector),\ \@ref(fig:role-company), and\ \@ref(fig:role-allocation) show the drop-down menu options for the sector, company role, and allocation role questions, respectively.

```{r demographics, out.width = "100%", fig.cap = "Demographics", fig.pos = "H"}
image_read(here("inst", "materials", "aggregation", "demographics.png")) %>% 
        image_trim()
```

```{r business, out.width = "100%", fig.cap = "Business-specific questionnaire", fig.pos = "H"}
image_read(here("inst", "materials", "aggregation", "business_information.png")) %>% 
        image_trim()
```

```{r sector, out.width = "100%", fig.cap = "Sector options", fig.pos = "H"}
image_read(here("inst", "materials", "aggregation", "sector.png")) %>% 
        image_trim()
```

```{r role-company, out.width = "100%", fig.cap = "Company role options", fig.pos = "H"}
image_read(here("inst", "materials", "aggregation", "role_company.png")) %>% 
        image_trim()
```

```{r role-allocation, out.width = "100%", fig.cap = "Allocation role options", fig.pos = "H"}
image_read(here("inst", "materials", "aggregation", "role_allocation.png")) %>% 
        image_trim()
```

# Instructions

Figure\ \@ref(fig:instructions) shows the instructions.

```{r instructions, out.width = "100%", fig.cap = "Instructions", fig.pos = "H"}
image_read(here("inst", "materials", "aggregation", "instructions.png")) %>% 
        image_trim()
```

## Project choice

Figures\ \@ref(fig:awareness-aware) and\ \@ref(fig:awareness-naive) show the webpage shown after the instructions to those in the aware and naive conditions, respectively. Figure\ \@ref(fig:joint-distribution) shows the joint presentation with distribution condition of the new experiment. Those in the separate presentation condition would see each project separately, and those in the no distribution condition would see them without the distribution. 
 
The gambles were generated from the following restrictions: 

1. Each gamble has a positive EV
2. Each gamble has a gain/loss ratio less than 2.25 [the median loss aversion coefficient from @tversky1992]
3. The entire portfolio has a probability of loss of less than 0.1
4. No identical gambles

```{r awareness-aware, out.width = "50%", fig.cap = "Awareness - Aware condition", fig.pos = "H"}
image_read(here("inst", "materials", "aggregation", "aware.png")) %>% 
        image_trim()
```

```{r awareness-naive, out.width = "50%", fig.cap = "Awareness - Naive condition", fig.pos = "H"}
image_read(here("inst", "materials", "aggregation", "naive.png")) %>% 
        image_trim()
```

```{r joint-distribution, out.width = "100%", fig.cap = "Joint presentation - Distribution present (cropped for space)", fig.pos = "H"}
image_read(here("inst", "materials", "aggregation", "joint_distribution.png")) %>% 
  image_trim() %>%
  image_crop("1485x1880+0+0")
```


## Follow up

After seeing the individual projects, participants would be asked three follow-up questions. Figure\ \@ref(fig:project-number) shows the project number question (maximum value is set to 20).
Figures\ \@ref(fig:portfolio-binary) and\ \@ref(fig:portfolio-number) ask participants whether they are willing to take all or none of the projects; and how many projects would they choose if they could pick randomly (maximum value is set to 20). Those in the distribution absent condition were asked the same questions, but without the distribution and its explanation.

```{r project-number, out.width = "100%", fig.cap = "Follow-up 1", fig.pos = "H"}
image_read(here("inst", "materials", "aggregation", "project_number.png")) %>% 
        image_trim()
```

```{r portfolio-binary, out.width = "100%", fig.cap = "Follow-up 2", fig.pos = "H"}
image_read(here("inst", "materials", "aggregation", "portfolio_binary.png")) %>% 
        image_trim()
```

```{r portfolio-number, out.width = "100%", fig.cap = "Follow-up 3", fig.pos = "H"}
image_read(here("inst", "materials", "aggregation", "portfolio_number.png")) %>% 
        image_trim()
```

\newpage

# References

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
