---
title             : "Anecdotes Experiment 2 - Plan"
shorttitle        : ""

note              : Created `r format(Sys.time())`

author: 
  - name          : "Shir Dekel"
  
floatsintext      : yes

bibliography      : '`r here::here("inst", "references.bib")`'
csl               : '`r system.file("apa.csl", package = "shiR")`'
documentclass     : "apa7"
classoption       : "man, donotrepeattitle"
header-includes:
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output: 
  papaja::apa6_pdf:
    includes: 
      in_header: "preamble.tex"
---

```{r setup, include = FALSE}
opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Addressing Experiment 1 limitations

- Limitation: only used negative anecdotes
    - Solution: add valence condition
        - Negative: anecdote is a case study of a failed project that is similar to
          the target project (as in Experiment 1)
        - Positive: anecdote is a case study of a successful project that is similar to
          the target project
- Limitation: unclear way to test the interaction effect
    - Solution: plan analysis in advance
        - Still unclear
        - Maybe subtract the anecdote conditions allocation from the statistics only
          condition allocation to a get a "corrected" allocation score, and then
          conduct a standard three-way ANOVA.
- Limitation: using the anecdote could be normative if it seems that it was
  chosen due to its similarity
    - Solution: clarify that the anecdotes were sampled randomly
        - Use similar wording to @hayes2019.
        
            > We asked a student to open a book on plants and animals at weak
            > pages and note the first three living things they came across
            > and whether or not those living things have the property in
            > question.
            >
            > This means the information you receive may not be the most
            > strong for making your judgment - by chance, the student will
            > sometimes select very dissimilar items, and sometimes very
            > similar ones.

# Summary

- Experiment 2 investigates the effects of anecdote alignment and valence on
  anecdotal bias.
- IVs
    - Similarity: low and high.
        - Within-subjects
    - Valence: low and high.
        - Within-subjects
    - Anecdote: statistics only, anecdote only, and combined.
        - Between-subjects anecdotes
        - Within-subjects statistics only
- DV
    - Allocation (0-100)
- Each participants is in one of two between-subjects anecdote conditions, and
  sees five displays (statistics only, and four anecdote displays).

# Hypotheses

- Statistics only condition will be higher (lower) than each anecdote condition for the
  negative (positive) valence condition.
- Main effect of similarity. 
- Main effect of anecdote (excluding statistics only).
- Three-way interaction, such that the effects are reversed between the valence conditions.
- See Figure\ \@ref(fig:plot-simulation-anecdotes-2)

```{r plot-simulation-anecdotes-2, fig.cap = "Anecdotes Experiment 2 predicted data"}
readd(plot_simulation_anecdotes_2)
```

\newpage

# References

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
