---
title             : "Anecdotes Experiment 2 - Plan"
shorttitle        : ""

note              : Created `r format(Sys.time())`

author: 
  - name          : "Shir Dekel"
  
floatsintext      : yes

bibliography      : '`r here::here("inst", "references.bib")`'
csl               : '`r system.file("apa.csl", package = "shiR")`'
documentclass     : "apa7"
classoption       : "man, donotrepeattitle"
header-includes:
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output: 
  papaja::apa6_pdf:
    includes: 
      in_header: "preamble.tex"
---

```{r setup, include = FALSE}
opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Changing argument

Initially, the argument was that people are over-relying on anecdotes, while
they should be using aggregated data instead. However, as Rob Goldstone’s
example suggests, there are situations in which an anecdote is so similar (e.g.,
an identical twin) that it would be unwise not to use the anecdote. As such, the
idea is to pivot to the argument to be that people might actually be sensitive
to the relevance of the anecdote. That is, our data suggests that they (arguably
wisely) use the anecdote when it seems to share causal structure, and use it
less when it doesn’t (even though it’s the same type of project). In fact,
people seem to actually integrate the anecdote with the statistical information.

Therefore, we can keep the anecdote descriptions the same as in Experiment 1
(i.e., either causally similar to the target, or not). Further, we do not need
to include any further descriptions of the pool of anecdotes (such as the limit
of similarity) other than the fact that it is large and anecdotes are randomly
sampled.

# Addressing Experiment 1 limitations

- Limitation: only used negative anecdotes
    - Solution: add valence condition
        - Negative: anecdote is a case study of a failed project that is similar to
          the target project (as in Experiment 1)
        - Positive: anecdote is a case study of a successful project that is similar to
          the target project
- Limitation: unclear way to test the interaction effect
    - Solution: compare the relevant simple effects.
        - For instance, low similarity combined vs. high similarity combined, and
          high similarity combined vs. statistics only. The two differences
          should imply the interaction.
- Limitation: using the anecdote could be normative if it seems that it was
  chosen due to its similarity
    - Solution: change argument to be about people's ability to use anecdotes
    when casual structure seems relevant, and to avoid them when it does not.
        - Still clarify that the anecdotes were sampled randomly [with similar
          wording to @hayes2019].
        - Change the follow-up relevance question to be something like "how much
          do you think the reason the case study failed is relevant to the
          performance of the target project"

# Summary

- Experiment 2 investigates the effects of anecdote alignment and valence on
  anecdotal bias.
- IVs
    - Similarity: low and high.
        - Within-subjects
    - Valence: low and high.
        - Within-subjects
    - Anecdote: statistics only, anecdote only, and combined.
        - Between-subjects anecdotes
        - Within-subjects statistics only
- DV
    - Allocation (0-100)
- Each participants is in one of two between-subjects anecdote conditions, and
  sees five displays (statistics only, and four anecdote displays).

# Hypotheses

- Statistics only condition will be higher (lower) than each anecdote condition for the
  negative (positive) valence condition.
- Main effect of similarity. 
- Main effect of anecdote (excluding statistics only).
- Three-way interaction, such that the effects are reversed between the valence conditions.
- See Figure\ \@ref(fig:plot-simulation-anecdotes-2)

```{r plot-simulation-anecdotes-2, fig.cap = "Anecdotes Experiment 2 predicted data"}
readd(plot_simulation_anecdotes_2)
```

\newpage

# References

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
