---
title             : "Anecdotes Experiment 1 - Results summary"
shorttitle        : ""

note              : Created `r format(Sys.time())`

author: 
  - name          : "Shir Dekel"
  
floatsintext      : yes

bibliography      : '`r here::here("inst", "references.bib")`'
csl               : '`r system.file("apa.csl", package = "shiR")`'
documentclass     : "apa7"
classoption       : "man, donotrepeattitle"
output: 
  papaja::apa6_pdf:
    includes: 
      in_header: "preamble.tex"
---

```{r setup, include = FALSE}
opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
loadd(descriptives_anecdotes_1)
loadd(results_anecdotes_1)
loadd(plot_anecdotes_1)
```

- Experiment 1 investigated the effect of alignment on the anecdotal bias
  effect.
- The anecdotal bias effect is usually seen by the difference in responses to a
condition that only involves statistics, and a condition that involves both
statistics and an anecdote.
- We were interested in whether this effect was moderated by the similar of the
  anecdote to the target.

# Participants

`r descriptives_anecdotes_1$apa` Table\ \@ref(tab:allocation) shows the condition allocation.

```{r allocation}
descriptives_anecdotes_1$condition_allocation_table %>% 
  apa_table("Group allocation to the between-subject variables of anecdote condition and alignment.")
```

# Results

- We found an interaction between anecdote condition and similarity (only when
  collapsing across the combined and enhanced conditions).
- Participants allocated more to the statistics only condition than the combined
 statistics + anecdote condition in the high similarity condition.
    - But not in the low similarity condition.
- See Figure\ \@ref(fig:plot-anecdotes-1).

``` {r plot-anecdotes-1, fig.cap = "Mean allocation to Project A (the target project). Error bars represent 95% confidence intervals."}
plot_anecdotes_1
```

# Limitations

- Anecdotes were all "negative" (meaning that were examples of a project that
  performed poorly).
    - Unclear if effects will be also seen for positive anecdotes, because
      previous literature in medical decision-making found effects only for
      negative anecdotes. This might be because people's baseline is "positive"
      health.
    - However, this is likely to be different in the business domain, because
      wealth can be more tangibly increased. 
- Unclear how to properly express the interaction statistically.
    - The statistics only condition is not a part of the crossed design, so
      cannot be tested in a standard ANOVA.
    - A statistics consultant suggested to simply conduct two t-tests (comparing
      statistics only to combined low similarity, and combined low similarity to
      combined high similarity), which should imply the interaction. But unclear
      if this will satisfy a reviewer.
- Using the anecdote may be normative if participants assume that the anecdote
  was chosen intentionally due to its similarity.
  - @hayes2019 found that participants' similarity-based inductions depend on
    whether they were told that the source information was randomly sampled or
    chosen intentionally.

\newpage

# References

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
