---
title             : "Aggregation Experiment 4 - Results summary"
shorttitle        : ""

note              : Created `r format(Sys.time())`

author: 
  - name          : "Shir Dekel"
  
floatsintext      : yes

bibliography      : '`r system.file("refs.bib", package = "shiR")`'
csl               : '`r system.file("apa.csl", package = "shiR")`'
documentclass     : "apa7"
classoption       : "man, donotrepeattitle"
output: 
  papaja::apa6_pdf:
    includes: 
      in_header: "preamble.tex"
---

```{r setup, include = FALSE}
opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
loadd(descriptives_aggregation_4)
loadd(results_aggregation_4)
loadd(plot_aggregation_4)
```

# Participants

`r descriptives_aggregation_4$apa` Table\ \@ref(tab:allocation) shows the condition allocation.

```{r allocation}
descriptives_aggregation_4$condition_allocation_table %>% 
  apa_table("Group allocation to the between-subject variable of awareness.")
```

# Results

Experiment 4 investigated the effect of "awareness" on project choice. The
"naive" condition attempted to encourage participants to focus on projects one
at a time and did not say how many projects there were. The "aware" condition
attempted to encourage participants to think of all 20 projects (by saying the
total number in the beginning, and notifying participants where they were in the
project order). The data were analysed using either a t-test (when the effect
involved comparison of proportion values), or a logistic regression (when the
effect involved binary choice).

## Project investment

Figures\ \@ref(fig:plot-choice-binary) and\ \@ref(fig:plot-choice-proportion)
show the choice and proportion data, respectively. The difference between
awareness conditions was not significant, both in the logistic regression
`r results_aggregation_4$choice$full_result[[2]]`, and in the t-test,
`r results_aggregation_4$proportion`.

```{r plot-choice-binary, fig.cap = "Mean project acceptance for the awareness effect."}
plot_aggregation_4$choice_binary
```

```{r plot-choice-proportion, fig.cap = "Mean proportion of project acceptance for the awareness effect."}
plot_aggregation_4$choice_proportion
```

Further, Figure\ \@ref(fig:plot-choice-trials) shows the choice data as a
function of the order of the project in the sequence. As Table\
\@ref(tab:similarity-project-order) shows, there were no main effects or interactions. 

```{r plot-choice-trials, fig.cap = "Mean project acceptance by awareness and trial."}
plot_aggregation_4$choice_trials
```

```{r similarity-project-order}
results_aggregation_4$awareness_project_order$table %>%
  apa_table("Logistic regression table of project acceptance by awareness and trial.")
```

## Follow-up

### Project expectation

We asked participants how many projects they expected to see. Figure\
\@ref(fig:plot-project-expectation) shows that those in the aware condition
reportedly expect to see more. However, this is likely to be due to the fact
that they were told how many projects there were.

```{r plot-project-expectation, fig.cap = "Number of projects participants expected to see, by condition"}
plot_aggregation_4$project_expectation
```

### Project number

We asked participants how many projects they think they saw. Figure\
\@ref(fig:plot-project-number) shows that overall people to correctly estimate
the number of projects, with more accuracy for those in the aware condition.

```{r plot-project-number, fig.cap = "Number of projects participants reported seeing, by condition"}
plot_aggregation_4$project_number
```

### Portfolio choice - binary

Participants were then asked if they would rather invest in all or none of the
projects. As Figure\ \@ref(fig:plot-portfolio-binary) shows, there was no
significant difference between awareness conditions in wanting to invest
in all of the projects,
`r results_aggregation_4$portfolio_binary$full_result[[2]]`.

```{r plot-portfolio-binary, fig.cap = "Mean choice of investing in all 10 projects for the awareness effect."}
plot_aggregation_4$portfolio_binary
```

### Portfolio choice - number

Subsequently, we asked participants how many projects they would invest in out
of the 10 that they saw. As Figure\ \@ref(fig:plot-portfolio-number) shows, the
difference between awareness conditions was not significant,
`r results_aggregation_4$portfolio_number`.

```{r plot-portfolio-number, fig.cap = "Mean number of projects chosen in the follow-up for the awareness effect."}
plot_aggregation_4$portfolio_number
```

## Gambles

Figures\ \@ref(fig:plot-trials) and\ \@ref(fig:plot-gamble-values) show that
overall people seemed to prefer gambles with higher probabilities of gain,
sometimes regardless of expected value or value of the gain.

```{r plot-trials, fig.cap = "Mean project acceptance for the 10 gambles. The format of the labels indicate: (gain probability, gain value; loss probability, loss value)."}
plot_aggregation_4$trials
```

```{r plot-gamble-values, fig.cap = "Mean project acceptance for the gambles' expected value, positive probability, and positive outcome."}
plot_aggregation_4$gamble_values
```
