---
title             : "Aggregation Experiment 4 - Results summary"
shorttitle        : ""

note              : Created `r format(Sys.time())`

author: 
  - name          : "Shir Dekel"
  
floatsintext      : yes

bibliography      : '`r system.file("refs.bib", package = "shiR")`'
csl               : '`r system.file("apa.csl", package = "shiR")`'
documentclass     : "apa7"
classoption       : "man, donotrepeattitle"
output: 
  papaja::apa6_pdf:
    includes: 
      in_header: "preamble.tex"
---

```{r setup, include = FALSE}
opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
loadd(descriptives_aggregation_4)
loadd(results_aggregation_4)
loadd(plot_aggregation_4)
```

# Participants

`r descriptives_aggregation_4$apa` Table\ \@ref(tab:allocation) shows the condition allocation.

```{r allocation}
descriptives_aggregation_4$allocation %>% 
  apa_table("Group allocation to the between-subject variables of awareness, presentation, and distribution.")
```

# Results

## Project investment

Figures\ \@ref(fig:plot-choice-binary) and\ \@ref(fig:plot-choice-proportion) show the choice and proportion data, respectively. The difference between similarity conditions was not significant, both in the logistic regression `r results_aggregation_4$choice$full_result[[2]]`, and in the t-test, `r results_aggregation_4$proportion`.

```{r plot-choice-binary, fig.cap = "Mean project acceptance for the similarity effect."}
plot_aggregation_4$choice_binary
```

```{r plot-choice-proportion, fig.cap = "Mean proportion of project acceptance for the similarity effect."}
plot_aggregation_4$choice_proportion
```

Further, as Figure\ \@ref(fig:plot-choice-trials) shows, it doesn't seem as if the previous awareness by trial effect was replicated.

```{r plot-choice-trials, fig.cap = "Mean project acceptance by similarity and trial."}
plot_aggregation_4$choice_trials
```

## Follow-up

### Project expectation

We asked participants how many projects they expected to see. Figure\ \@ref(fig:plot-project-expectation) shows that overall people to correctly estimate the number of projects, with more accuracy for those in the aware condition.

```{r plot-project-expectation, fig.cap = "Number of projects participants expected to see, by condition"}
plot_aggregation_4$project_expectation
```

### Project number

We asked participants how many projects they think they saw. Figure\ \@ref(fig:plot-project-number) shows that overall people to correctly estimate the number of projects, with more accuracy for those in the aware condition.

```{r plot-project-number, fig.cap = "Number of projects participants reported seeing, by condition"}
plot_aggregation_4$project_number
```

### Portfolio choice - binary

Participants were then asked if they would rather invest in all or none of the projects. As Figure\ \@ref(fig:plot-portfolio-binary) shows, the difference between presentation conditions was not significant, `r results_aggregation_4$portfolio_binary$full_result[[2]]`. 

```{r plot-portfolio-binary, fig.cap = "Mean choice of investing in all 10 projects for the similarity effect."}
plot_aggregation_4$portfolio_binary
```

### Portfolio choice - number

Subsequently, we asked participants how many projects they would invest in out of the 10 that they saw. As Figure\ \@ref(fig:plot-portfolio-number) shows, the difference between presentation conditions was not significant, `r results_aggregation_4$portfolio_number`.

```{r plot-portfolio-number, fig.cap = "Mean number of projects chosen in the follow-up for the similarity effect."}
plot_aggregation_4$portfolio_number
```

## Gambles

Figures\ \@ref(fig:plot-trials) and\ \@ref(fig:plot-gamble-values) show the overall people seemed to prefer gambles with higher probabilities of gain, sometimes regardless of expected value or value of the gain.

```{r plot-trials, fig.cap = "Mean project acceptance for the 10 gambles. The format of the labels indicate: (gain probability, gain value; loss probability, loss value)."}
plot_aggregation_4$trials
```

```{r plot-gamble-values, fig.cap = "Mean project acceptance for the gambles' expected value, positive probability, and positive outcome."}
plot_aggregation_4$gamble_values
```
