---
title             : "Aggregation Experiment 3 - Materials"
shorttitle        : ""

note              : Created `r format(Sys.time())`

author: 
  - name          : "Shir Dekel"
  
floatsintext      : yes

bibliography      : '`r system.file("refs.bib", package = "shiR")`'
csl               : '`r system.file("apa.csl", package = "shiR")`'
documentclass     : "apa7"
classoption       : "man, donotrepeattitle"
output: 
  papaja::apa6_pdf:
    includes: 
      in_header: "preamble.tex"
---

```{r setup, include = FALSE}
opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

Experiment 3 tests the similarity effect. Participants in the low similarity condition will see 10 projects, each from a different industry. Participants in the high similarity condition will set 10 projects from the same industry (the specific industry will be randomly assigned), each with a different variation. For instance, 10 oil well projects, each from a different location. The instructions are the same as the previous "naive awareness" condition.

```{r instructions-experiment3, out.width = "100%", fig.cap = "Instructions - Experiment 3", fig.pos = "H"}
here("inst", "materials", "experiment3", "instructions_experiment3.png") %>% 
  image_read()
```

```{r include = FALSE}
file_paths_materials_experiment3 <- 
  here("inst", "materials", "experiment3")

paths <- file_paths_materials_experiment3 %>% 
  list.files() %>% 
  str_match("project_choice_experiment3_(.*).png") %>% 
  na.omit() %>% 
  split(rep(1:ncol(.), each = nrow(.)))

src <- 
  paths %>% 
  pmap(
    ~ c(
      '```{r project-choice-experiment3-{{.y}}, out.width = "100%", fig.cap = "Example {{.y}} project (order of sentences randomised)", fig.pos = "H"}',
      'image_read(file.path(file_paths_materials_experiment3, "{{.x}}"))',
      '```'
    ) %>% 
      knit_expand(text = .) # needs `text = `
  )

res <- 
  knit_child(text = unlist(src)) # only works when knitting
```

`r res`
