---
title             : "Aggregation Experiment 3 - Materials"
shorttitle        : ""

note              : Created `r format(Sys.time())`

author: 
  - name          : "Shir Dekel"
  
floatsintext      : yes

bibliography      : '`r system.file("refs.bib", package = "shiR")`'
csl               : '`r system.file("apa.csl", package = "shiR")`'
documentclass     : "apa7"
classoption       : "man, donotrepeattitle"
output: 
  papaja::apa6_pdf:
    includes: 
      in_header: "preamble.tex"
---

```{r setup, include = FALSE}
opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
loadd(dir_materials_experiment3)
```

Experiment 3 tests the similarity effect. Participants in the low similarity condition will see 10 projects, each from a different industry. Participants in the high similarity condition will set 10 projects from the same industry (the specific industry will be randomly assigned), each with a different variation. For instance, 10 oil well projects, each from a different location. Description sentence order is randomised. See below screenshots of the instructions, project descriptions (for brevity only one variation per project is shown), and follow-up questions.

```{r include = FALSE}
file_name_materials_experiment3 <-
    get_file_name_materials_experiment3()
  
file_path_materials_experiment3 <- 
  get_file_path_materials(dir_materials_experiment3, file_name_materials_experiment3)
  
src <- 
  list(
  file_name_materials_experiment3 %>% 
    str_replace_all("_", "-"),
  file_name_materials_experiment3 %>% 
    str_replace_all("_", " ") %>% 
    str_to_sentence(),
  file_path_materials_experiment3
) %>% 
  pmap(
    function(chunk_name, caption, path) 
      c(
      '```{r {{chunk_name}}, out.width = "100%", fig.cap = "{{caption}}", fig.pos = "H"}',
      'image_read("{{path}}")',
      '```'
    ) %>% 
      knit_expand(text = .) # needs `text = `
  )

res <- 
  knit_child(text = unlist(src)) # only works when knitting
```

`r res`
