### Method

#### Participants

`r descriptives_aggregation_1$apa`

#### Materials

```{r materials-aggregation-1}
  instructions_doc <- aggregation::instructions %>% 
    str_replace_all("</p><p>|</p> <p>|<br>", "\n\n >") %>% 
    str_remove_all("<p>|</p>")
  project_doc <- aggregation::projects$highA[[1]] %>% 
    str_c(aggregation::project_question) %>% 
    str_replace_all(c("<b>|</b>" = "**",
                      "<p>|</p>" = "\n\n")) %>% 
    str_c("Yes \\_\\_ No \\_\\_")
```

##### Instructions

Participants saw the following instructions:

> `r instructions_doc`

##### Risky investment task

```{r}
losses <- aggregation::dist_rep$outcomes < 0 
p_loss <- aggregation::dist_rep$probs[losses] %>% 
  sum()

chance_pos <- 0.5 %>% 
  rep(10)
pos <- 200 %>% 
  rep(10)
dif <- 300
outcomes <- shiR::getoutcomes(pos, dif)
dist_rep_samuelson <- shiR::getpoisbinom(prob = chance_pos,
                                         outcomes = outcomes %>% 
                                           sort())

losses_samuelson <- dist_rep_samuelson$outcomes < 0 
p_loss_samuelson <- dist_rep_samuelson$probs[losses_samuelson] %>%
    sum()
```

In the risky investment task, participants saw 10 short descriptions of business projects, and asked whether they would invest in that project or not. Each description included the name of the hypothetical business, the amount they forecast the project to cost, the amount they forecast the project to make, and probabilities for these forecasts. We constructed these projects to appear attractive when aggregated, and unattractive when segregated [see @langer2001]. Project values were different for each project, but followed a set of constraints for each project's EV and loss aversion coefficient ($\lambda$), and the probability of any loss given the outcome distribution of all 10 projects ($P(loss)$):

1.  $\text{EV} > 0$;

2.  $\lambda < 2$; and

3.  $P(loss) < 0.1$.

As such, each project cannot be considered to be a loss under expected value theory, but also would not be an easy choice for investment, because of the low $\lambda$. Further,since people are especially sensitive to loss probabilities [@zeisberger2020; @kahneman1979], an arbitrarily low $P(loss)$ was chosen to make investment in the complete set of projects seem attractive (see Figure\ \@ref(fig:aggregation-outcome).[^5] Below is an example of a description of a project in this task:

[^5]:  The actual probability of a loss given the outcome distribution we used was `r p_loss`. This was calculated by summing all probabilities in the Poisson binomial distribution in Figure\ \@ref(fig:aggregation-outcome) whose outcomes were less than zero. For comparison, $P(loss)$ = `r p_loss_samuelson` for 10 plays of the @samuelson1963 gamble.

> `r project_doc`

In the low similarity condition, these project descriptions were all about one type of projects and were all from the same business. In the high similarity condition, each project was from a different industry. In the joint presentation condition, the 10 projects were all displayed on the one webpage, whereas in the separate presentation condition each was displayed on a different webpage. Participants in the aware condition read the following before their separate presentation display: "`r aggregation::awareness["aware"]`" Those in the naive condition simply proceeded without this message. Note, the financial and probability values were identical regardless of condition, and the order of each set of 10 projects was randomised.

##### Outcome distribution decision

Participants were asked if they would invest in the last 10 projects they saw and were provided with a graph of the outcome probability distribution of the 10 projects, seen in Figure\ \@ref(fig:aggregation-outcome).[^6]

[^6]:  This Poisson binomial distribution was calculated using the R package `poibin`, which uses calculations described in @hong2013.

```{r aggregation-outcome, fig.cap = "The outcome distribution of the 10 gambles used in the experiment."}
shiR::plotdist(x = aggregation::dist_rep$outcomes, y = aggregation::dist_rep$probs, xlab = "Outcome ($ million)")
```

##### Negative EV gambles

We wanted to make sure that participants were generally making decisions that were in line with EV theory and that our sample was not abnormally risk tolerant. As such, we presented participants two project decisions that had a negative EV. Out of the `r descriptives_aggregation_1$total*2` negative EV gambles included (two per participant), all but `r results_aggregation_1$neg_sum_apa` were rejected.

#### Procedure

Participants read the instructions and completed the risky investment task, first in the separate presentation condition, and then in the joint condition. Participants then made the outcome distribution decision and subsequently completed the negative EV gambles.

