### Method

#### Participants

`r descriptives_aggregation_1$apa` Table\ \@ref(tab:allocation-aggregation-1) shows the condition allocation.

```{r allocation-aggregation-1}
descriptives_aggregation_1$condition_allocation_table %>%
  apa_table("Experiment 1 group allocation.")
```

#### Materials

##### Instructions {#instructions-aggregation-1}

Participants were shown the instructions in
Figure\ \@ref(fig:instructions-aggregation-1).

(ref:instructions-aggregation-1) Experiment 1 instructions.

```{r instructions-aggregation-1, fig.cap = "(ref:instructions-aggregation-1)"}
here(
  "inst",
  "materials",
  "aggregation",
  "experiment1",
  "instructions.png"
) %>%
  image_read() %>%
  image_trim()
```

##### Risky investment task {#task-aggregation-1}

In the risky investment task, participants saw 10 short descriptions of business
projects, and were asked whether they would invest in that project or not. Each
description included the name of the hypothetical business, the amount they
forecast the project to cost, the amount they forecast the project to make, and
probabilities for these forecasts. I constructed these projects to appear
attractive when aggregated, and unattractive when segregated [see @langer2001].
Project values were different for each project, but followed a set of
constraints for each project's EV and loss aversion coefficient ($\lambda$), and
the probability of any loss given the outcome distribution of all 10 projects
($P(loss)$):
 
1.  $\text{EV} > 0$;

2.  $\lambda < 2.25$; and

3.  $P(loss) < 0.1$.

As such, each project cannot be considered to be a loss under expected value
theory, but also would not be an easy choice for investment, because of the low
$\lambda$ [made to be lower than the median loss aversion coefficient calculated
in @tversky1992]. Further, since people are especially sensitive to loss
probabilities [@zeisberger2020; @kahneman1979], an arbitrarily low $P(loss)$ was
chosen to make investment in the complete set of projects seem attractive (see
Figure\ \@ref(fig:project-choice-aggregated-aggregation-1)).[^5]
Figure\ \@ref(fig:project-choice-aggregation-1) shows an example of a
description of a project in this task.

[^5]: The actual probability of a loss given the outcome distribution I used
    was `r gambles_aggregation_1$loss_prob`. This was calculated by summing all
    probabilities in the Poisson binomial distribution in
    Figure\ \@ref(fig:project-choice-aggregated-aggregation-1) whose outcomes were less
    than zero. For comparison, $P(loss)$ =
    `r results_aggregation_1$loss_prob_samuelson` for 10 plays of the
    @samuelson1963 gamble.

(ref:project-choice-aggregation-1) Example of a project choice display in Experiment 1.

```{r project-choice-aggregation-1, fig.cap = "(ref:project-choice-aggregation-1)"}
here(
  "inst",
  "materials",
  "aggregation",
  "experiment1",
  "project_choice_oil-well_separate_similarity_low_1.png"
) %>%
  image_read() %>%
  image_trim()
```

In the low similarity condition, these project descriptions were all about one
type of project (in this case an oil wel project) and were all from the same
business. In the high similarity condition, each project was from a different
industry. In the joint presentation condition, the 10 projects were all
displayed on the one webpage, whereas in the separate presentation condition
each was displayed on a different webpage. Participants in the aware condition
saw the display shown in Figure\ \@ref(fig:awareness-aware-aggregation-1) before
their separate presentation display. Those in the naive condition simply
proceeded without this message. Note, the financial and probability values were
identical regardless of condition, and the order of each set of 10 projects was
randomised.

(ref:awareness-aware-aggregation-1) The display seen by those in the aware
condition of Experiment 1.

```{r awareness-aware-aggregation-1, fig.cap = "(ref:awareness-aware-aggregation-1)"}
here(
  "inst",
  "materials",
  "aggregation",
  "experiment1",
  "awareness_aware.png"
) %>%
  image_read() %>%
  image_trim()
```

##### Outcome distribution decision

Participants were asked if they would invest in the last 10 projects they saw
and were provided with a graph of the outcome probability distribution of the 10
projects, seen in
Figure\ \@ref(fig:project-choice-aggregated-aggregation-1).[^6]

[^6]: This Poisson binomial distribution was calculated using the R package
    `poibin`, which uses calculations described in @hong2013.

(ref:project-choice-aggregated-aggregation-1) The outcome distribution of the 10
gambles used in the experiment.

```{r project-choice-aggregated-aggregation-1, fig.cap = "(ref:project-choice-aggregated-aggregation-1)"}
here(
  "inst",
  "materials",
  "aggregation",
  "experiment1",
  "project_choice_aggregated.png"
) %>%
  image_read() %>%
  image_trim()
```

##### Follow-up gambles

###### Negative EV gambles

I wanted to make sure that participants were generally making decisions that
were in line with EV theory and that our sample was not abnormally risk
tolerant. As such, I presented participants two project decisions that had a
negative EV. Out of the `r descriptives_aggregation_1$total*2` negative EV
gambles included (two per participant), all but
`r results_aggregation_1$neg_sum_apa` were rejected.

###### @samuelson1963 gambles

I showed participants the original @samuelson1963 gamble, asked them whether they
would accept 10 of that gamble, and whether they would accept those 10 given the
associated outcome distribution. I then showed them the same three questions,
but using outcome magnitudes that were similar to the ones in the risky
investment task. That is, instead of /$100, /$100 million.

###### @redelmeier1992 gambles

I then showed participants the same three types of gambles (single, 10, and
aggregated), but with the values from the gambles that were used by
@redelmeier1992.

#### Procedure

Participants read the instructions and completed the risky investment task,
first in the separate presentation condition, and then in the joint condition.
Participants then made the outcome distribution decision, responded to the 11
follow-up gambles.
