### Results

A three-way ANOVA was conducted to investigate the effects of similarity,
awareness, and presentation on the proportion of participants' decision to
invest in the 10 projects. As seen in
Figure\ \@ref(fig:plot-aggregation-1-awareness), participants invested more when they
were told that there will be 10 projects, compared to when they were not told
this, `r results_aggregation_1$awareness`. As seen in
Figure\ \@ref(fig:plot-aggregation-1-presentation), participants invested more when
viewing the projects jointly, compared to when they viewed them separately,
`r results_aggregation_1$presentation`. Although there was no main effect of
similarity, `r results_aggregation_1$alignment`, the interaction between
similarity and presentation was significant,
`r results_aggregation_1$alignment_presentation` (see
Figure\ \@ref(fig:plot-aggregation-1-alignment-presentation)). Specifically, the
presentation effect seems stronger in the high similarity condition,
`r results_aggregation_1$highjoint_highseparate`, than in the low similarity
condition, `r results_aggregation_1$lowjoint_lowseparate`.

(ref:plot-aggregation-1-awareness) Mean proportions of decisions to invest in
each set of 10 projects, by awareness conditions. Error bars represent 95%
confidence intervals.

```{r plot-aggregation-1-awareness, fig.cap = "(ref:plot-aggregation-1-awareness)"}
plot_aggregation_1$awareness
```

(ref:plot-aggregation-1-presentation) Mean proportions of decisions to invest in
each set of 10 projects, by presentation conditions. Error bars represent 95%
confidence intervals.

```{r plot-aggregation-1-presentation, fig.cap = "(ref:plot-aggregation-1-presentation)"}
plot_aggregation_1$presentation
```

(ref:plot-aggregation-1-alignment-presentation) Mean proportions of decisions to
invest in each set of 10 projects, by similarity and presentation conditions.
Error bars represent 95% confidence intervals.

```{r plot-aggregation-1-alignment-presentation, fig.cap = "(ref:plot-aggregation-1-alignment-presentation)"}
plot_aggregation_1$alignment_presentation
```

A paired-samples t-test was conducted to compare participants' decision to
invest in the 10 projects while seeing an aggregated distribution, and their
decisions to invest in the projects individually, without the distribution.
Participants invested in the 10 projects more when seeing the distribution both
in the separate presentation phase,
`r results_aggregation_1$individual_aggregated$separate`; and in the joint
presentation phase, `r results_aggregation_1$individual_aggregated$joint`.
