### Results

#### Project choice

I conducted a three-way ANOVA to investigate the effects of similarity,
awareness, and presentation on the proportion of participants' decision to
invest in the 10 projects. As seen in
Figure\ \@ref(fig:plot-aggregation-1-awareness), participants invested more when they
were told that there will be 10 projects, compared to when they were not told
this, `r results_aggregation_1$awareness`. As seen in
Figure\ \@ref(fig:plot-aggregation-1-presentation), participants invested more when
viewing the projects jointly, compared to when they viewed them separately,
`r results_aggregation_1$presentation`. Although there was no main effect of
similarity, `r results_aggregation_1$alignment`, the interaction between
similarity and presentation was significant,
`r results_aggregation_1$alignment_presentation` (see
Figure\ \@ref(fig:plot-aggregation-1-alignment-presentation)). Specifically, the
presentation effect seems stronger in the high similarity condition,
`r results_aggregation_1$highjoint_highseparate`, than in the low similarity
condition, `r results_aggregation_1$lowjoint_lowseparate`.

(ref:plot-aggregation-1-awareness) Mean proportions of decisions to invest in
each set of 10 projects, by awareness conditions. Error bars represent 95%
confidence intervals.

```{r plot-aggregation-1-awareness, fig.cap = "(ref:plot-aggregation-1-awareness)"}
plot_aggregation_1$awareness
```

(ref:plot-aggregation-1-presentation) Mean proportions of decisions to invest in
each set of 10 projects, by presentation conditions. Error bars represent 95%
confidence intervals.

```{r plot-aggregation-1-presentation, fig.cap = "(ref:plot-aggregation-1-presentation)"}
plot_aggregation_1$presentation
```

(ref:plot-aggregation-1-alignment-presentation) Mean proportions of decisions to
invest in each set of 10 projects, by similarity and presentation conditions.
Error bars represent 95% confidence intervals.

```{r plot-aggregation-1-alignment-presentation, fig.cap = "(ref:plot-aggregation-1-alignment-presentation)"}
plot_aggregation_1$alignment_presentation
```

#### Outcome distribution {#outcome-distribution-aggregation-3}

A paired-samples t-test was conducted to compare participants' decision to
invest in the 10 projects while seeing an aggregated distribution, and their
decisions to invest in the projects individually, without the distribution.
Participants invested in the 10 projects more when seeing the distribution both
in the separate presentation phase,
`r results_aggregation_1$individual_aggregated$separate`; and in the joint
presentation phase, `r results_aggregation_1$individual_aggregated$joint`.

However, I subsequently discovered that the code that generated this
distribution mistakenly flipped the outcome values. This means that although it
appeared from the distribution that the propability of loss was
`r gambles_aggregation_1$loss_prob`, the actual probability of loss of the
underlying values given the correct distribution was
`r gambles_aggregation_1$loss_prob_correct`. As such, even though I found an
effect of distribution, it is unclear if the effect was driven by participants
actually accurately assessing the riskiness of the individual gambles, and
therefore showing a difference between the isolated and aggregated gambles in a
normative way.

#### Trial-by-trial analysis

I conducted exploratory analyses into the possible effects of the manipulations
on a trial-by trial basis. Figure\ \@ref(fig:plot-aggregation-1-trials) shows
proportions of project acceptance across all conditions and trials.

(ref:plot-aggregation-1-trials) Proportion of project acceptance by trial,
similarity, awareness, and presentation conditions. LOESS is used for smoothing
over trials, and the shading represents 95% confidence intervals.

```{r plot-aggregation-1-trials, fig.cap = "(ref:plot-aggregation-1-trials)"}
plot_aggregation_1$trials
```

The key findings is in the separate presentation. As
Figure\ \@ref(fig:plot-aggregation-1-trials-separate-awareness) shows, in the separate
condition people are more likely to accept projects over the 10 trials, but this
interacts with awareness,
`r results_aggregation_1$full_result$awareness1_project_order`. Specifically,
the relationship between choice and trial is significant in the aware condition,
`r results_aggregation_1$trials_separate_awareness_slope$aware`; but not in the naive condition,
`r results_aggregation_1$trials_separate_awareness_slope$naive`.

(ref:plot-aggregation-1-trials-separate-awareness) Proportion of project
acceptance in the separate presentation condition, by trial, and awareness
conditions. LOESS is used for smoothing over trials, and the shading
represents 95% confidence intervals.

```{r plot-aggregation-1-trials-separate-awareness, fig.cap = "(ref:plot-aggregation-1-trials-separate-awareness)"}
plot_aggregation_1$trials_separate_awareness
```
