### Results {#results-aggregation-2}

#### Project investment

The project investment data was analysed in two ways: as binary choice per trial
(using logistic regression), and as proportions of choice per participant (using
t-test). In each case I compared the relevant comparison condition to the same
control condition (separate naive distribution absent).
Figures\ \@ref(fig:plot-aggregation-2-choice)
and\ \@ref(fig:plot-aggregation-2-proportion) show the choice and proportion data,
respectively. The difference between presentation conditions was not
significant, both in the logistic regression
`r results_aggregation_2$choice$presentation$full_result[[2]]`, and in the
t-test, `r results_aggregation_2$proportion$presentation`. Similarly, the
difference between awareness conditions was not significant, both in the
logistic regression `r results_aggregation_2$choice$awareness$full_result[[2]]`,
and in the t-test, `r results_aggregation_2$proportion$awareness`. However,
those that that saw a distribution tended to choose to invest significantly more
(`r results_aggregation_2$distribution_mean$present$choice`) than those that did
not see a distribution
(`r results_aggregation_2$distribution_mean$absent$choice`), seen both in the
logistic regression, `r results_aggregation_2$choice_distribution`, and the
t-test `r results_aggregation_2$proportion$distribution`.

(ref:plot-aggregation-2-choice) Mean project acceptance for the presentation,
awareness, and distribution effects. Note, the condition on the left of each
effect is the reference condition (separate presentation, naive awareness,
distribution absent). As such, it is identical for the three effects.

```{r plot-aggregation-2-choice, fig.cap = "(ref:plot-aggregation-2-choice)"}
plot_aggregation_2$choice_binary
```

(ref:plot-aggregation-2-proportion) Mean proportion of project acceptance for
the presentation, awareness, and distribution effects. Note, the condition on
the left of each effect is the reference condition (separate presentation, naive
awareness, distribution absent). As such, it is identical for the three effects.

```{r plot-aggregation-2-proportion, fig.cap = "(ref:plot-aggregation-2-proportion)"}
plot_aggregation_2$choice_proportion
```

Further, as Figure\ \@ref(fig:plot-aggregation-2-choice-trials) shows, it
doesn't seem as if the previous awareness by trial effect was replicated.

(ref:plot-aggregation-2-choice-trials) Mean project acceptance for separate
presentation, distribution absent condition, by awareness and trial.

```{r plot-aggregation-2-choice-trials, fig.cap = "(ref:plot-aggregation-2-choice-trials)"}
plot_aggregation_2$choice_trials
```

#### Follow-up

##### Project number

We asked participants how many projects they think they saw.
Figure\ \@ref(fig:plot-aggregation-2-project-number) shows that overall people
to correctly estimate the number of projects, with more accuracy for those in
the aware condition.

(ref:plot-aggregation-2-project-number) Number of projects participants reported
seeing, by condition.

```{r plot-aggregation-2-project-number, fig.cap = "(ref:plot-aggregation-2-project-number)"}
plot_aggregation_2$project_number
```

##### Portfolio choice - binary

Participants were then asked if they would rather invest in all or none of the
projects. As Figure\ \@ref(fig:plot-aggregation-2-portfolio-binary) shows, the difference
between presentation conditions was not significant,
`r results_aggregation_2$portfolio_binary$presentation$full_result[[2]]`. The
awareness effect was also not significant,
`r results_aggregation_2$portfolio_binary$awareness$full_result[[2]]`. However,
those that that saw a distribution chose to invest in all 10 projects
significantly more
(`r results_aggregation_2$distribution_mean$present$portfolio_binary`) than those
that did not see a distribution
(`r results_aggregation_2$distribution_mean$absent$portfolio_binary`),
`r results_aggregation_2$portfolio_binary_distribution`.

(ref:plot-aggregation-2-portfolio-binary) Mean choice of investing in all 10
projects for the presentation, awareness, and distribution effects. Note, the
condition on the left of each effect is the reference condition (separate
presentation, naive awareness, distribution absent). As such, it is identical
for the three effects.

```{r plot-aggregation-2-portfolio-binary, fig.cap = "(ref:plot-aggregation-2-portfolio-binary)"}
plot_aggregation_2$portfolio_binary
```

##### Portfolio choice - number

Subsequently, we asked participants how many projects they would invest in out
of the 10 that they saw. As Figure\ \@ref(fig:plot-aggregation-2-portfolio-number) shows, the
difference between presentation conditions was not significant,
`r results_aggregation_2$portfolio_number$presentation`. The awareness effect was
also not significant, `r results_aggregation_2$portfolio_number$awareness`.
However, those that that saw a distribution chose to invest in significantly
more projects than those that did not see a distribution,
`r results_aggregation_2$portfolio_number$distribution`.

(ref:plot-aggregation-2-portfolio-number) Mean number of projects chosen in the
follow-up for the presentation, awareness, and distribution effects. Note, the
condition on the left of each effect is the reference condition (separate
presentation, naive awareness, distribution absent). As such, it is identical
for the three effects.

```{r plot-aggregation-2-portfolio-number, fig.cap = "(ref:plot-aggregation-2-portfolio-number)"}
plot_aggregation_2$portfolio_number
```

#### Gambles

Figures\ \@ref(fig:plot-aggregation-2-trials)
and\ \@ref(fig:plot-aggregation-2-gamble-values) show the overall people seemed
to prefer gambles with higher probabilities of gain, sometimes regardless of
expected value or value of the gain.

(ref:plot-aggregation-2-trials) Mean project acceptance for the 10 gambles. The
format of the labels indicate: (gain probability, gain value; loss probability,
loss value).

```{r plot-aggregation-2-trials, fig.cap = "(ref:plot-aggregation-2-trials)"}
plot_aggregation_2$trials
```

(ref:plot-aggregation-2-gamble-values) Mean project acceptance for the gambles'
expected value, positive probability, and positive outcome.

```{r plot-aggregation-2-gamble-values, fig.cap = "(ref:plot-aggregation-2-gamble-values)"}
plot_aggregation_2$gamble_values
```
