---
title             : "Anecdotes Experiment 2 - Results summary"
shorttitle        : ""

note              : Created `r format(Sys.time())`

author: 
  - name          : "Shir Dekel"
  
floatsintext      : yes

bibliography      : '`r system.file("refs.bib", package = "shiR")`'
csl               : '`r system.file("apa.csl", package = "shiR")`'
documentclass     : "apa7"
classoption       : "man, donotrepeattitle"
output: 
  papaja::apa6_pdf:
    includes: 
      in_header: "preamble.tex"
---

```{r setup, include = FALSE}
opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
loadd(descriptives_anecdotes_2)
loadd(results_anecdotes_2)
loadd(plot_anecdotes_2)
```

# Participants

`r descriptives_anecdotes_2$apa` Table\ \@ref(tab:condition-allocation-table)
shows the condition allocation.

```{r condition-allocation-table}
descriptives_anecdotes_2$condition_allocation_table %>%
  apa_table("Group allocation to the between-subject anecdote conditions.")
```

# Results

## Allocations

### Overall effect of manipulations

As seen in Figure\ \@ref(fig:plot-allocations), the similarity $\times$ valence
$\times$ anecdote interaction (excluding the statistics-only condition) was
significant, `r results_anecdotes_2$three_way`.

### Similarity manipulation check

The similarity manipulation worked as expected, with the negative valence
anecdote-only low similarity condition being allocated significantly more than
those in the high similarity condition,
`r results_anecdotes_2$anecdotes_only_similarity$valence_negative`. In the
positive valence condition, those in the high similarity condition allocation
significantly more than those in the low similarity condition,
`r results_anecdotes_2$anecdotes_only_similarity$valence_positive`

### Effect of statistics

When in the negative valence condition, participants allocated more to the high
similarity combined project than those in the high similarity anecdote-only
condition, `r results_anecdotes_2$similarity_high_anecdote$valence_negative`.
When in the positive valence condition, they allocated more to high similarity
anecdote-only condition than those in the high similarity combined condition,
`r results_anecdotes_2$similarity_high_anecdote$valence_positive`.

### Anecdotal bias moderated by similarity

To investigate whether anecdotal bias was moderated by similarity, we compared
allocations between the combined high and low similarity conditions and the
statistics-only condition. We found that in the negative valence condition,
participants allocated more to the statistics-only condition than to the
combined high similarity condition,
`r results_anecdotes_2$combined$valence_negative$similarity_high_statistics_only`.
Participants in the combined low similarity allocated more than when they saw
the combined high similarity display,
`r results_anecdotes_2$combined$valence_negative$similarity_high_similarity_low`.
However, the difference between responses to the statistics-only projects and the
combined low similarity projects was not significant,
`r results_anecdotes_2$combined$valence_negative$similarity_low_statistics_only`.

In the positive valence, allocations were higher in the statistics-only
condition than in the combined low similarity condition,
`r results_anecdotes_2$combined$valence_positive$similarity_high_statistics_only`.
Allocations were also higher in the combined high similarity condition than in
the combined low similarity condition,
`r results_anecdotes_2$combined$valence_positive$similarity_high_similarity_low`.
Further, allocations were higher in the statistics-only condition than in the
combined high similarity condition.

```{r plot-allocations, fig.cap = "Mean project allocation for all conditions."}
plot_anecdotes_2
```

## Ratings

### Similarity manipulation check

Our similarity manipulation seems to have worked, with participants rating
anecdotes in the high similarity conditions as more similar to the target than
those in the low similarity condition,
`r results_anecdotes_2$similarity_rating_similarity`.

### Allocation is influenced by perceived similarity

As hypothesised, allocation was influenced by perceived similarity. That is, in
the negative valence condition, there was a negative correlation between
allocation and similarity rating,
`r results_anecdotes_2$allocation_similarity_rating$negative_high_low`.
However, in the positive valence condition,
there was a positive correlation between allocation and similarity rating,
`r results_anecdotes_2$allocation_similarity_rating$positive_high_low`.

### The relationship between allocation and specific-relevance is moderated by similarity

In the negative valence condition, there was a significant difference between
the slopes of the high and low similarity conditions,
`r results_anecdotes_2$allocation_specific_relevance$high_low_negative`.
In the low similarity condition, allocation and specific-relevance rating were
not correlated,
`r results_anecdotes_2$allocation_specific_relevance$negative_loweffect`,
whereas, in the low similarity condition, they were correlated negatively
`r results_anecdotes_2$allocation_specific_relevance$negative_higheffect`.

In the positive valence condition, there was a significant difference between
the slopes of the high and low similarity conditions,
`r results_anecdotes_2$allocation_specific_relevance$high_low_positive`.
In the low similarity condition, allocation and specific-relevance rating were
not correlated,
`r results_anecdotes_2$allocation_specific_relevance$positive_loweffect`,
whereas, in the low similarity condition, they were correlated positively
`r results_anecdotes_2$allocation_specific_relevance$positive_higheffect`.

### People do not consider general-relevance in their allocation

There were no significant correlations between allocation and general-relevance
rating.



