---
title             : "Alignment Experiment 8 - Plan"
shorttitle        : ""

note              : Created `r format(Sys.time())`

author: 
  - name          : "Shir Dekel"
  
floatsintext      : yes

bibliography      : '`r system.file("refs.bib", package = "shiR")`'
csl               : '`r system.file("apa.csl", package = "shiR")`'
documentclass     : "apa7"
classoption       : "man, donotrepeattitle"
header-includes:
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output: 
  papaja::apa6_pdf:
    includes: 
      in_header: "preamble.tex"
---

```{r setup, include = FALSE}
opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
loadd(materials_alignment_8)
```

# Summary

- Experiment 8 (previously called Experiment 4 in the context of the article,
  but it is the 8th alignment experiment of the thesis) investigates the effects
  of alignment, reliability type, NPV amount, and reliability amount on
  allocations.
- IVs
    - Alignment: low and high
        - Between-subjects
    - Reliability type: implicit and explicit
        - Between-subjects
    - Reliability amount: low and high
        - Within-subjects
    - NPV amount: vector of five approximately equally spaced integers
      between 400-900
        - Within-display
        - Slightly different between each display
- DVs
    - Allocation (0-100)
    - Ranking (1-5)

# Hypotheses

## Omnibus

- Alignment $\times$ reliability amount $\times$ reliability type $\times$ NPV
  amount interaction
- See Figure\ \@ref(fig:plot-simulation-alignment-8).

## Specifically

- *Explicit reliability, high alignment*: NPV amount $\times$ reliability amount interaction.
    - **Participants will rely on NPV when told it is reliable, but will rely on
      intrinsic features when told NPV is unreliable.**
- *Explicit reliability, low alignment*: main effect of NPV amount.
    - **Participants will rely on NPV regardless of stated reliability.**
- *Implicit reliability*: no effects.
    - **Participants will allocate equally across projects.**

```{r plot-simulation-alignment-8, fig.cap = "Alignment Experiment 8 predicted data"}
readd(plot_simulation_alignment_8)
```

# Materials

- Instructions
    - One version for each reliability type condition.
    - Includes a test of basic NPV understanding.
        - Also acts as a sort of attention check as, though it is required to
          answer, the response should only be one of two letters.
- Each participant will see two project displays.
    - One for each reliability amount condition.
    - Each display will have one of two sets of five projects (10 individual
      projects total).
    - Each display has a table describing the projects in the set, with ranking and
      allocation inputs.
    - Before each display, participants will see an "interstitial" page, whose
      role is 1. to introduce the next display, and 2. an attention check (not required to answer, so can be skipped if the interstitial text isn't read).
- The following are counterbalanced:
    - The association of reliability amount and project set (two variations).
    - The association of business name with NPV (five latin square variations).
    - Project variation (five variations per alignment condition).
        - For high alignment this means the project type.
        - For low alignment this means the intrinsic feature variant for the
          relevant project type.
- The following are randomised:
    - Table column order.
    - Project display order.
- The below figures show a sample of the possible project displays
  participants will see.
    - For the low alignment displays, only one "variation" is shown here.
        - Across the two reliability amount conditions this shows all 10
          possible project types.
        - Both reliability type conditions are shown.
            - All that differs here is the way the NPV is described.
    - For the high alignment displays, all five "variations" are shown.
        - For both reliability amount conditions.

## Screenshots

```{r include = FALSE}
file_name_materials <-
  get_file_name_materials_alignment_8()

file_path_materials <-
  get_file_path_materials(materials_alignment_8, file_name_materials)

figure_captions <-
  file_name_materials %>%
  str_replace_all(
    c(
      "_" = " ",
      "allocation" = "allocation -",
      "alignment" = "alignment:",
      " reliability type" = ", reliability type:",
      " reliability amount" = ", reliability amount:",
      " variation" = ", variation:"
    )
  ) %>%
  str_c(".") %>%
  str_to_sentence()

src <-
  list(
    file_name_materials %>%
      str_replace_all("_", "-"),
    figure_captions,
    file_path_materials
  ) %>%
  pmap(
    function(chunk_name, caption, path) {
      c(
        '```{r {{chunk_name}}, out.width = "100%", fig.cap = "{{caption}}", fig.pos = "H"}',
        'image_read("{{path}}") %>% image_trim()',
        "```"
      ) %>%
        knit_expand(text = .)
    } # needs `text = `
  )

res <-
  knit_child(text = unlist(src)) # only works when knitting
```

`r res`
