---
title             : "Alignment Experiment 8 - Materials"
shorttitle        : ""

note              : Created `r format(Sys.time())`

author: 
  - name          : "Shir Dekel"
  
floatsintext      : yes

bibliography      : '`r system.file("refs.bib", package = "shiR")`'
csl               : '`r system.file("apa.csl", package = "shiR")`'
documentclass     : "apa7"
classoption       : "man, donotrepeattitle"
header-includes:
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output: 
  papaja::apa6_pdf:
    includes: 
      in_header: "preamble.tex"
---

```{r setup, include = FALSE}
opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
loadd(materials_alignment_8)
```

- Experiment 8 (previously called Experiment 4 in the context of the article, but it is the 8th alignment experiment of the thesis) investigates the effects of alignment (between-subjects), reliability type (between-subjects), and reliability amount (within-subjects) on allocations. 

Hypotheses

- More reliance on NPV in low alignment compared to high alignment, but only in the explicit reliability condition.
- An interaction between reliability amount and NPV amount (within-display), but only in the explicit reliability condition.

```{r include = FALSE}
file_name_materials <-
  get_file_name_materials_alignment_8()

file_path_materials <-
  get_file_path_materials(materials_alignment_8, file_name_materials)

src <-
  list(
    file_name_materials %>%
      str_replace_all("_", "-"),
    file_name_materials %>%
      str_replace_all("_", " ") %>%
      str_to_sentence(),
    file_path_materials
  ) %>%
  pmap(
    function(chunk_name, caption, path) {
      c(
        '```{r {{chunk_name}}, out.width = "100%", fig.cap = "{{caption}}", fig.pos = "H"}',
        'image_read("{{path}}") %>% image_trim()',
        "```"
      ) %>%
        knit_expand(text = .)
    } # needs `text = `
  )

res <-
  knit_child(text = unlist(src)) # only works when knitting
```

`r res`
