---
title             : "Alignment Experiment 8 - Results summary"
shorttitle        : ""

note              : Created `r format(Sys.time())`

author: 
  - name          : "Shir Dekel"
  
floatsintext      : yes

bibliography      : '`r system.file("refs.bib", package = "shiR")`'
csl               : '`r system.file("apa.csl", package = "shiR")`'
documentclass     : "apa7"
classoption       : "man, donotrepeattitle"
output: 
  papaja::apa6_pdf:
    includes: 
      in_header: "preamble.tex"
---

```{r setup, include = FALSE}
opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
loadd(descriptives_alignment_8)
loadd(results_alignment_8)
loadd(plot_alignment_8)
```

# Participants

`r descriptives_alignment_8$apa` Table\ \@ref(tab:condition-allocation-table) shows the condition allocation.

```{r condition-allocation-table}
descriptives_alignment_8$condition_allocation_table %>%
  apa_table("Group allocation to the between-subject variables of alignment and reliability type.")
```

# Results

## Summary

- Explicit reliability
    - Participants used (didn't use) NPV when told explicitly that is reliable
      (unreliable).
    - However, participants relied on NPV more regardless of reliability when
      projects were dissimilar, compared to when they were similar.
- Implicit reliability
    - Participants did not use ranges to moderate allocations
    - However, they did use the NPV mid-point.
    - They also relied on NPV more when projects were dissimilar than when they
      were similar.

## Detailed

We found evidence for all but one of the hypothesised effects.

1. The four way interaction (alignment $\times$ reliability amount $\times$ NPV
  amount $\times$ reliability type) was significant,
  `r results_alignment_8$four_way`.
  - See Figure\ \@ref(fig:plot-four-way).
2. The three-way interaction (reliability amount $\times$ NPV amount $\times$
  reliability type) in the high alignment condition was significant,
  `r results_alignment_8$alignment_high_three_way`.
3. The three-way interaction (alignment $\times$ reliability amount $\times$
  NPV amount) in the explicit reliability condition was significant,
  `r results_alignment_8$reliability_type_explicit_three_way`.
4. The NPV amount $\times$ reliability type (averaging over reliability amount)
  in the low alignment condition was significant,
  `r results_alignment_8$alignment_low_two_way`.
5. The association between allocation and NPV amount for those in the explicit
  reliability high alignment condition was significantly stronger for those in
  the high reliability condition, than for those in the low reliability
  condition,
  `r results_alignment_8$alignment_high_reliability_type_explicit_reliability_amount`.
6. The association between allocation and NPV amount for those in the
  explicit low reliability condition was significantly stronger for those in the
  low alignment condition, than for those in the high alignment condition,
  `r results_alignment_8$reliability_type_explicit_reliability_amount_low_alignment`.
7. The association between allocation and NPV amount for those in the low
  alignment condition was significantly stronger for those in the explicit
  reliability condition, than for those in the implicit reliability condition
  (averaging over reliability amount),
  `r results_alignment_8$alignment_low_reliability_type`.
8. The association between allocation and NPV amount for those in the implicit
  reliability condition was significantly "equivalent" between those in the
  low and high alignment conditions (averaging over reliability amount),
  `r results_alignment_8$reliability_type_implicit_alignment_null`.
    - However, a post-hoc comparison suggests a significant difference from zero
    (with Bonferroni adjustment),
    `r results_alignment_8$reliability_type_implicit_alignment`.
9. The association between allocation and NPV amount for those in the implicit
  reliability condition was significantly "equivalent" between those in the low
  and high reliability conditions for both those in the low alignment
  `r results_alignment_8$alignment_low_reliability_type_implicit_reliability_amount_null`
  and high alignment conditions
  `r results_alignment_8$alignment_high_reliability_type_implicit_reliability_amount_null`.

```{r plot-four-way, fig.cap = "Mean project allocation for all conditions."}
plot_alignment_8$four_way
```
